Historical Methods 1640-1828

### 2018-09-01 inst/examples/201808-HistoricalMethods-Overview.Rmd
ok

@@

### Total overview

Records in the final data set used in the analyses (years ```r min(df0$publication_year)```-```r max(df0$publication_year)```):

Percentage of non-empty entries for each field (per catalogue).

@@

Number of unique and all publishers per catalogue.

```{r publishers_fen, echo=FALSE, message=FALSE, warning=FALSE}
kable(top(fen, field, 10, "data.frame", round = 1))
```

```{r publishers_kun, echo=FALSE, message=FALSE, warning=FALSE}
kable(top(kun, field, 10, "data.frame", round = 1))
```

Number of unique and all authors per catalogue.

```{r authors_fen, echo=FALSE, message=FALSE, warning=FALSE}
kable(top(fen, field, 10, "data.frame", round = 1))
```

```{r authors_kun, echo=FALSE, message=FALSE, warning=FALSE}
kable(top(kun, field, 10, "data.frame", round = 1))
```

Page count variation.

```{r pagecount, echo=FALSE, message=FALSE, warning=FALSE, fig.width=10, figh.height=3}
p <- ggplot(df0) +
       geom_histogram(aes(x = pagecount)) + 
       labs(x = "Page count (n)",
            y = "Frequency (n)") +
       scale_x_log10(breaks = c(1, 10, 100, 1000)) +       
       facet_grid(. ~ catalog)
print(p)
```

Paper consumption estimates.

```{r paper, echo=FALSE, message=FALSE, warning=FALSE, fig.width=10, figh.height=3}
p <- ggplot(df0) +
       geom_histogram(aes(x = paper)) + 
       labs(x = "Paper (sheets)",
            y = "Frequency (n)") +
       scale_x_log10(breaks = c(1, 10, 100, 1000)) +       
       facet_grid(. ~ catalog)
print(p)
```

```{r year, echo=FALSE, message=FALSE, warning=FALSE, fig.width=10, figh.height=3}
p <- ggplot(df0) +
       geom_histogram(aes(x = publication_year)) + 
       labs(x = "Publication year",
            y = "Frequency (n)") +
       scale_x_log10(breaks = c(1, 10, 100, 1000)) +       
       facet_grid(. ~ catalog)
print(p)
```

Number of unique and all languages per catalogue.

```{r languages_fen, echo=FALSE, message=FALSE, warning=FALSE}
kable(top(fen, field, 10, "data.frame", round = 1))
```

```{r languages_kun, echo=FALSE, message=FALSE, warning=FALSE}
kable(top(kun, field, 10, "data.frame", round = 1))
```

Number of unique and all publication places per catalog.

```{r places_fen, echo=FALSE, message=FALSE, warning=FALSE}
kable(top(fen, field, 10, "data.frame", round = 1))
```

```{r places_kun, echo=FALSE, message=FALSE, warning=FALSE}
kable(top(kun, field, 10, "data.frame", round = 1))
```

Percent of unique and all gatherings per catalogue.

>>>>

Records in the final data set used in the analyses:

Data availability for the key fields analyzed in this work (%):

@@

Number of unique authors and all documents with author information:

```{r authors_fen, echo=FALSE, message=FALSE, warning=FALSE}
tab <- top(fen, field, 10, "data.frame", round = 1)
colnames(tab) <- gsub("author", "Author", colnames(tab))
kable(tab)
```

```{r authors_kun, echo=FALSE, message=FALSE, warning=FALSE}
tab <- top(kun, field, 10, "data.frame", round = 1)
colnames(tab) <- gsub("author", "Author", colnames(tab))
kable(tab)
```

Proportion (%) of unique gatherings and all documents with gatherings information:

Number of unique publishers and all documents with publisher information:

```{r publishers_fen, echo=FALSE, message=FALSE, warning=FALSE}
tab <- top(fen, field, 10, "data.frame", round = 1)
colnames(tab) <- gsub("publisher", "Publisher", colnames(tab))
kable(tab)
```

```{r publishers_kun, echo=FALSE, message=FALSE, warning=FALSE}
tab <- top(kun, field, 10, "data.frame", round = 1)
colnames(tab) <- gsub("publisher", "Publisher", colnames(tab))
kable(tab)
```

Page count variation per gatherings. The variants have been combined (2long/2to; 4long/4to; 8long/8vo; 12long/12mo). Documents with missing gatherings are not shown.

```{r pagecount, echo=FALSE, message=FALSE, warning=FALSE, fig.width=20, figh.height=1}
df <- df0
df$gatherings <- gsub("^2long", "2fo", df$gatherings)
df$gatherings <- gsub("4long", "4to", df$gatherings)
df$gatherings <- gsub("8long", "8vo", df$gatherings)
df$gatherings <- gsub("12long", "12mo", df$gatherings)
df <- df[which(!df$gatherings == "NA"), ]
df <- subset(df, !is.na(pagecount))
df$gatherings <- order_gatherings(df$gatherings)

cols <- default_colors("gatherings", levels(df$gatherings))

p <- ggplot(df) +
       geom_histogram(aes(x = pagecount,
		    group = gatherings,       
                    #y = ..count../sum(..count..),
                    fill = gatherings),
                    color = "black",
		    alpha = 0.5
		    ) + 
       labs(x = "Page count (n)",
            y = "Frequency (n)") +
       scale_x_log10(breaks = c(1, 10, 100, 1000)) +
       scale_y_log10(breaks = c(1, 10, 100, 1000)) +
       scale_fill_manual(values = unname(cols)) +       
       facet_grid(catalog ~ gatherings) +
       guides(fill = "none") + 
       labs(y = "Frequency (n)") +
       theme(
         axis.text = element_text(size=10)
             )
print(p)
```

Paper consumption estimates per gatherings (sheets per document). The variants have been combined (2long/2to; 4long/4to; 8long/8vo; 12long/12mo). Documents with missing page count estimates are not shown.

```{r paper, echo=FALSE, message=FALSE, warning=FALSE, fig.width=20, figh.height=1}
x <- c(.01, .1, 1, 10, 100, 1000)
df <- df0
df$gatherings <- gsub("^2long", "2fo", df$gatherings)
df$gatherings <- gsub("4long", "4to", df$gatherings)
df$gatherings <- gsub("8long", "8vo", df$gatherings)
df$gatherings <- gsub("12long", "12mo", df$gatherings)
df <- df[which(!df$gatherings == "NA"), ]
df <- subset(df, !is.na(paper))
df$gatherings <- order_gatherings(df$gatherings)
cols <- default_colors("gatherings", levels(df$gatherings))

p <- ggplot(df) +
       geom_histogram(aes(x = paper/1e3, # Remove print run estimates
		    group = gatherings,       
                    fill = gatherings),
                    color = "black",
		    alpha = 0.5
		    ) +
       scale_fill_manual(values = unname(cols)) + 		    
       labs(x = "Paper per document (sheets)",
            y = "Frequency (n)") +
       scale_y_log10(breaks = c(1, 10, 100, 1000)) +
       scale_x_log10(breaks = x,
           labels=scales::trans_format('log10', scales::math_format(10^.x))) + 
       facet_grid(catalog ~ gatherings) +
       guides(fill = "none") + 
       labs(y = "Frequency (n)") +
       theme(
         axis.text = element_text(size=10)
             )

print(p)

```

```{r year, echo=FALSE, message=FALSE, warning=FALSE, fig.width=10, figh.height=3}
p <- ggplot(df0) +
       geom_histogram(aes(x = publication_year)) + 
       labs(x = "Publication year",
            y = "Frequency (n)") +
       # scale_x_log10(breaks = c(1, 10, 100, 1000)) +       
       facet_grid(. ~ catalog)
print(p)
```

Number of unique languages and all documents with language information.

```{r languages_fen, echo=FALSE, message=FALSE, warning=FALSE}
tab <- top(fen, field, 10, "data.frame", round = 1)
colnames(tab) <- gsub("language", "Language", colnames(tab))
kable(tab)
```

```{r languages_kun, echo=FALSE, message=FALSE, warning=FALSE}
tab <- top(kun, field, 10, "data.frame", round = 1)
colnames(tab) <- gsub("language", "Language", colnames(tab))
kable(tab)
```

Number of unique publication places and all documents with publication place information.

```{r places_fen, echo=FALSE, message=FALSE, warning=FALSE}
tab <- top(fen, field, 10, "data.frame", round = 1)
colnames(tab) <- gsub("publication_place", "Publication place", colnames(tab))
kable(tab)
```

```{r places_kun, echo=FALSE, message=FALSE, warning=FALSE}
tab <- top(kun, field, 10, "data.frame", round = 1)
colnames(tab) <- gsub("publication_place", "Publication place", colnames(tab))
kable(tab)
```

@@
